The Place of the Local Group in the Cosmic Web

### 2014-04-28 paper/main.tex
updating the whole text

\altaffiltext{1}{Uni A}
\altaffiltext{2}{Uni B}
\altaffiltext{3}{Uni C}
\begin{abstract}
This
\end{abstract}

@@

\citet{2013ApJ...767L...5F} also study MW-M31 pairs in numerical
simulations finding the typical quantities characterizing the orbital
parameters of the LG are rare among typical pairs, but not enough to
challenge the \lcdm model. 
Another definition of LG analogues is made by
\citet{2008MNRAS.384.1459L}, but despite differences ocurr in the
definitions and resulting fraction of LG analogues, all are in
agreement with a low frequency of these pairs. 
%lw08 also look lg analogues

@@

Paper is organized ...

\section{Simulation and web finding algorithm}
\label{sec:Simulation}

@@

\begin{equation}
T_{ij} = \frac{\partial^2 \phi}{\partial r_i \partial r_j}, 
\end{equation}
where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
coordiates and $\phi$ is the gravitational potential renormalized to
follow the following Poisson equation $\nabla\phi=\delta$ where
$\delta$ is the matter overdensity.

This tensor is real and symmetric, which means that can be
diagonalized. We note the eigenvalues $\lambda_1\geq \lambda_2\geq
\lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
$\hat{e}_2$ and $\hat{e}_3$. The web classification compares each one
of the three eigenvalues to a threshold value $\lambda_{\rm th}$. If the three, two, one or zero eigenvalues are larger than this threshold the region es classified as peak, filament, sheet or void, respectively.

@@

The ellipticity and the prolatenes are quantities that measure the
relative strength of the three eigenvalues. They are defined as
follows

\begin{equation}
e= \frac{\lambda_3 - \lambda_1}{2(\lambda_1 + \lambda_2 + \lambda_3)}, 
\end{equation}

\begin{equation}
p= \frac{\lambda_1 + \lambda_3 - 2\lambda_2}{2(\lambda_1 + \lambda_2 +
  \lambda_3)}.
\end{equation}

@@

\section{Local Group Analogues}

To construct a sample of the MW-M31 pairs at $z\approx 0$, we use a
series of simulation snapshots  at $z<0.1$ (i.e. in the last $\approx
1.3$ Gyr before present) spaced by $\approx 150-250$ Myr. This is done
because a particular configuration of MW and M31 is transient and
would correspond to a relatively small number of systems at one
snapshot. By using multiple snapshots we can increase the sample of
systems in such configuration during a period of time in which secular
cosmological evolution is small.

@@

We define two samples according to the tolerance in the selection constraints:
A sample named $2\sigma$, correspondig to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly. The number of pairs in each sample
is $46$ and $120$ respectively, notice we have less pairs than in
\citet{lganalogues} results, since we removed pairs which are too
close at $z=0$, i.e. their virial radii overlaps, also we removed a
couple pairs who merged or change their mass more than $20\%$ at
present time since they were detected at $z<0.1$.

@@

\subsection{Pairs in Filaments and Sheets}

The first result we explore is the kind of environment occupied by
our LGs. We find that LGs in the restricted $2\sigma$ and $3\sigma$
samples prefer by large to be in filaments and sheets. Almost $\sim 50\%$ of the
pairs in both cases can be found in filaments while $\sim 40\%$ can be
found in sheets. This proportion is in stark contrast to the
environments for the general pair sample. In that case only $\sim
27\%$ and $\sim 33\%$ can be found in filaments and sheets,
repectively. There is a considerable fraction of pairs that are
located in peaks ($\sim 25\%$) and voids ($\sim 15\%$). These results
and the exact numbers are presented in Table \ref{table:web_type}.

@@

The next result is related to the matter overdensity for the LG
samples. Figure \ref{fig:density} shows that the range of
overdensities for the general pair sample spans almost two orders of
magnitude from underdense regions $\delta<0$ to high density regions
$\delta\sim 30$, with a distribution peaking around $\delta \sim
0$. In contrast the $2\sigma$ and $3\sigma$ samples are located within
a narrower range of overdensities $0.0<\delta<4.0$ peaking at $\delta
\sim 1.5$. These values are consistent with the fact that these
samples are mostly found in filaments and sheets.

In Figure \ref{fig:FA} we show the integrated distribution for the
Fractional Anisotropy in the tree samples. The General Sample clusters
towards values of ${\mathrm FA}\sim 1.0$, while the $2\sigma$ and
$3\sigma$ prefer values around $0.6$.

In Figure \ref{fig:delta_FA} we present a joint scatter plot for the
overdensity and fractional anisotropy. For clarity we only include the
general and $3\sigma$ samples. In this plane we observe from the general
sample that there are broad correlations between the overdensity and
the fractional anisotropy.

@@

\begin{table}
\begin{center}
\begin{tabular}{lccc}\hline\hline
Sample & $\langle\hat{e}_1\cdot \hat{n}\rangle$ & $\langle\hat{e}_2\cdot \hat{n}\rangle$ & $\langle\hat{e}_3\cdot \hat{n}\rangle$\\\hline
2$\sigma$ & 0.56 & 0.53 &  0.33\\
3$\sigma$ & 0.51 & 0.51 &  0.46\\
General & 0.54 & 0.52 & 0.40\\\hline
\end{tabular}
\caption{Average values for the cosinus between the three eigenvectors and the vector normal to the orbital plane.
\label{table:mu}}
\end{center}
\end{table}

>>>>

\altaffiltext{1}{Uni A}
\altaffiltext{2}{Uni B}
\altaffiltext{3}{Uni C}
\begin{abstract}
In this Letter we explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$ CDM cosmology.
We use a description for the cosmic web that uses the Hessian of the
gravitational potential to classify a nieghborhodd in the simulation
as either peak, sheet, filament or voids. We find that the LG pairs
are preferentially located in filaments and sheets. Locally their
locations are also located in a narrow range of overdensity
$0<\delta<4$, ellipticity $0.2<e<1.0$ and prolateness
$-0.5<p<0.5$. Furthermore we find a strong anti-alignment between the
LG angular momentum vector and the filament lines and the sheet 
planes.  
\end{abstract}

@@

\citet{2013ApJ...767L...5F} also studied MW-M31 pairs in numerical
simulations finding the typical quantities characterizing the orbital
parameters of the LG are rare among typical pairs, but not enough to
challenge the \lcdm model. 
Another definition of LG analogues is made by
\citet{2008MNRAS.384.1459L}, but despite differences ocurr in the
definitions and resulting fraction of LG analogues, all are in
agreement with a low frequency of these pairs. 
%lw08 also look lg analogues

@@

This Letter is organized as follows. In Section \ref{sec:simulation}
we present the N-body cosmological simulation and the algorithm to
define the cosmic web, next in \ref{sec:lg_analogues} we describe the
sample of LG analogues extracted from the simulation. In
Section \ref{sec:results} we presents our results to continue with a
discussion about their implications for our Local Group in Section
\ref{sec:discussion} to finally conclude in Section
\ref{sec:conclusions}.

\section{Simulation and web finding algorithm}
\label{sec:simulation}

@@

\begin{equation}
T_{ij} = \frac{\partial^2 \phi}{\partial r_i \partial r_j}, 
\end{equation}
%
where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
coordiates and $\phi$ is the gravitational potential renormalized to
follow the following Poisson equation $\nabla\phi=\delta$ where
$\delta$ is the matter overdensity.

This tensor is real and symmetric, which means that can be
diagonalized. We note the eigenvalues as $\lambda_1\geq \lambda_2\geq
\lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
$\hat{e}_2$ and $\hat{e}_3$. The web classification compares each one
of the three eigenvalues to a threshold value $\lambda_{\rm th}$. If
the three, two, one or zero eigenvalues are larger than this threshold
the region es classified as peak, filament, sheet or void,
respectively.

@@

@@

We use the matter overdensity, ellipticity and the prolatenes to characterize
the relative strength of the three eigenvalues. These quantities are
defined in terms of the eigenvalues as follows

\begin{equation}
\delta = \lambda_1 + \lambda_2 + \lambda_3,
\end{equation}

\begin{equation}
e= \frac{\lambda_3 - \lambda_1}{2(\lambda_1 + \lambda_2 + \lambda_3)}, 
\end{equation}
%
\begin{equation}
p= \frac{\lambda_1 + \lambda_3 - 2\lambda_2}{2(\lambda_1 + \lambda_2 +
  \lambda_3)}.
\end{equation}

We are also interested in measuring the alignment of the LG halos with
respect to the cosmic web. To this end we characterize each LG pair by
the vector that is normal to the orbital plane, which is defined by
the position and velocities of each halo with respect to the center of
mass.

\section{Local Group Analogues}
\label{sec:lg_analogues}

To construct a sample of the MW-M31 pairs at $z\approx 0$, we use a
series of simulation snapshots  at $z<0.1$ (i.e. in the last $\approx
1.3$ Gyr before present) spaced by $\approx 150-250$ Myr. This is done
because a particular configuration of MW and M31 is transient and
corresponds to a relatively small number of systems at one
snapshot. By using multiple snapshots we can increase the sample of
systems in such configuration during a period of time in which secular
cosmological evolution is small.

@@

We define two samples according to the tolerance in the selection constraints:
A sample named $2\sigma$, correspondig to LG analogues constrained by
two times the observational errors in the orbital values (radial
velocity, tangential velocity, and separation), and a more relaxed
sample named $3\sigma$ for LG analogues constrained by three times
observational errors accordingly. The number of pairs in each sample
is $46$ and $120$ respectively, notice we have less pairs than in
\citet{lganalogues} results, since we removed pairs which are too
close at $z=0$, i.e. their virial radii overlaps, also we removed a
couple pairs who merged or change their mass more than $20\%$ at
present time since they were detected at $z<0.1$.  We also have a
general sample which...

@@

\subsection{The prefered environment for LGs}

The first result we explore is the kind of environment occupied by
our LGs. We find that the LGs in the general sample are located across
all different evironment without any strong preferences; $1/3$  are
located in sheets, $1/4$ in peaks, $1/4$ in filaments and the remaning
$1/6$ in voids.

The situation in the restricted $2\sigma$ and $3\sigma$ samples is very
different. By large the LGs in these samples are located in
filaments and sheets. In both samples, $\sim 50\%$ of the
pairs can be found in filaments while $\sim 40\%$ are in
in sheets.

These absolute numbers in each environment for each sample are
presented in Table \ref{table:web_type}.

@@

We now describe the preferred place of the LG samples in terms of the
overdensity, ellipticiy and anisotropy as defined in Section
\ref{sec:simulation}.

Figure \ref{fig:density} shows that the range of overdensities for the
general pair sample spans almost two orders of magnitude from
underdense regions $\delta<0$ to high density regions $\delta\sim 30$,
with a distribution peaking around $\delta \sim 0$. In contrast the
$2\sigma$ and $3\sigma$ samples are located within a narrower range of
overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1.5$. This is
consistent with the fact that these samples are mostly found in
filaments and sheets.

Figure \ref{fig:ELL_PROL} presents the cumulative distribution for
the ellipticity and prolateness. The general sample presents a wide
range in ellipticity that can range from $-30<e<30$. For the $2\sigma$
and $3\sigma$ samples most of the pairs are now located in a narrow
range for ellipticities in the range $0.1<e<1.0$. This condition on
the ellipticity together with the fact that $\delta>0$ implies that
the prolateness in these samples must be bounded by
$-1.0<p<1.0$. We actually find that they most of the pairs are bounded
to an even narrower range $0.5<p<0.5$.

Figure \ref{fig:delta_FA} shows two panels with the joint scatter plot
for the ellipticity and the prolateness as a function of the
overdensity. For clarity we only include the general and $3\sigma$
samples. In the left panel (ellipticity) we see the a simple cut in
the overdensity is not enough to explain the narrow ranges in the
ellipticity; the LG pairs in the $3\sigma$ sample are located towards
low ellipticity values. In the right panel (prolateness) we find a
similar situation; a cut in the overdensity would produced a wider
distribution in prolateness values than the one featured by the
$3\sigma$ sample.

@@

%\begin{table}
%\begin{center}
%\begin{tabular}{lccc}\hline\hline
%Sample & $\langle\hat{e}_1\cdot \hat{n}\rangle$ & $\langle\hat{e}_2\cdot \hat{n%}\rangle$ & $\langle\hat{e}_3\cdot \hat{n}\rangle$\\\hline
%2$\sigma$ & 0.56 & 0.53 &  0.33\\
%3$\sigma$ & 0.51 & 0.51 &  0.46\\
%General & 0.54 & 0.52 & 0.40\\\hline
%\end{tabular}
%\caption{Average values for the cosinus between the three eigenvectors and the %vector normal to the orbital plane.
%\label{table:mu}}
%\end{center}
%\end{table}
